### 2021-03-19 README.Rmd
added my logo to readme
added links
update Rmd for README

# aracari

@@

The goal of aracari is to ...

## Installation

You can install the released version of aracari from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("aracari")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("javirudolph/aracari")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(aracari)
## basic example code
```

What is special about using `README.Rmd` instead of just `README.md`? You can include R chunks like so:

```{r cars}
summary(cars)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub!

>>>>

# aracari <img src="images/aracari.png" align="right" height="139" />

@@

Access the

- [seed dispersal paper](https://javirudolph.github.io/aracari/paper/paper.html) and the [figures](https://javirudolph.github.io/aracari/paper/figures_tables.html)
- [animal movement paper](https://javirudolph.github.io/aracari/movement_paper/rudolph_ch2.html)  
- [distributions paper](https://javirudolph.github.io/aracari/distributions_paper/rudolph_distributions.html)

---
## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("javirudolph/aracari")
```
